### 2014-03-16 src/analysis.Rnw
Fixes from Amin
Better graphs

% \begin{figure*}[t]
% <<x.per.sel.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
% ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
% # o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
% # ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
% #   stat_boxplot(geom ='errorbar')+
% #   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
% # 
% # o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
% # ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
% #   stat_boxplot(geom ='errorbar')+
% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
% # 
% # o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
% # ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
% #   stat_boxplot(geom ='errorbar')+
% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
% # 
% # o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
% # ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
% #   stat_boxplot(geom ='errorbar')+
% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
% @
% \caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
% \label{fig:xroundsel}
% \end{figure*}
%

@@

ggplot(df, aes(mutant.reduction, sd.reduction)) +
   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
   geom_point(aes(size=sqr, color=type)) + myopts
ggplot(df, aes(mutant.reduction, sd.reduction)) +
   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
   geom_point(aes(shape=sampling, color=type)) + myopts
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}

>>>>

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
o.xp.sample$type <- factor(o.xp.sample$type, levels=c('project','class','method','line'))
ggplot(subset(o.xp.sample, reduction < 100), aes(factor(power), reduction, fill=type, dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + #facet_wrap(~type) +
  myopts +
  #xlab(label=expression(frac(all,sample))) +
  xlab(label=expression(all%/%sample)) +
  ylab('reduction') +
  #theme(legend.position="none") +
  opts(title="sample(x)")
# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
# 
# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
# 
# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
# 
# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Original set $R^2 > 0.90$.}
\label{fig:powerplot}
\end{figure*}

@@

#ggplot(df, aes(mutant.reduction, sd.reduction)) +
#   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
#   geom_point(aes(size=sqr, color=type)) + myopts
ggplot(df, aes(mutant.reduction, sd.reduction)) +
   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
   geom_point(aes(shape=sampling, color=type)) + myopts
@
\caption{The mean reduction of mutants vs its standard deviation. Original set, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ is shown here. }
%\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times \sigma_{red} > \mu_{red}$ is shown here. }
\label{fig:fullimgsize}
\end{figure*}
